\documentclass[DIN, pagenumber=false, parskip=half,%
               fromalign=right, 
               fromrule=false]{scrlttr2}


\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% do not indent the signature
\renewcommand*{\raggedsignature}{\raggedright} 

% the sender:
\setkomavar{fromname}{Phu Nguyen}
\setkomavar{fromaddress}{Berlin School of Economics and Law \\ Badensche Straße 52 \\ 10825 Berlin}
\setkomavar{fromemail}{\href{mailto:phu.nguyen@hwr-berlin.de}{phu.nguyen@hwr-berlin.de}}
\setkomavar{signature}{Phu Nguyen}

\begin{document}
 
% the receiver:
\begin{letter}{The Business School, RMIT Vietnam \\
               702 Nguyen Van Linh Boulevard \\
               District 7, Ho Chi Minh City, Vietnam}

%===================================


\opening{}
\vspace{-1cm}
\textbf{Visiting Researcher Opportunity at RMIT Vietnam.}\\\\
\textbf{Dear Sir/Madam,}

I hope this letter finds you well. I am writing to express my interest in visiting \textit{RMIT Vietnam} as a visiting researcher for one week in April 2025. As a \textit{Research Associate} at the \textit{Berlin School of Economics and Law}, my research focuses on \textit{digital supply chains and resilience}. I believe that collaboration with your institution, particularly the \textit{Logistics and Supply Chain Management Research Cluster}, would be mutually beneficial.  

I would be delighted to contribute insights from my work on product-level networks to identify nexus materials (currently under second-round review in \textit{Omega}) and on rethinking material shortages (in progress, targeting \textit{Strategic Management Journal}). Additionally, I can present my work under the supervision of \href{https://scholar.google.de/citations?hl=de&user=yxK6B_oAAAAJ}{Prof. Dmitry Ivanov} as part of \href{https://accurateproject.eu/}{an EU-funded project} focused on developing digital supply chain twins for Airbus Atlantic, Continental, and Tronico.  

My visit will be self-funded, and I would sincerely appreciate any accommodation support that may be available. I would also be grateful for any guidance regarding the necessary procedures.  

I have attached my CV for your reference and look forward to the opportunity for academic exchange at \textit{RMIT Vietnam}. Thank you for your time and consideration.  

\closing{Sincerely,}

%===================================

\end{letter}
 
\end{document}
